---
title: "Chapter3_Dec_20"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#3.6.3 Multiple Linear Regression

```{r}
library (MASS)
library (ISLR)
lm.fit <- lm(data = Boston, medv~lstat+age)
summary(lm.fit)
```
#for see all variables

```{r}
lm.fit <- lm(medv~. , data=Boston)
summary(lm.fit)
summary(lm.fit)$r.sq
#summary(lm.fit)$sigma gives us the RSE
summary(lm.fit)$sigma
```

```{r}
#install.packages("car")
library (car)
vif(lm.fit)
#all variables except age

lm.fit1=lm(medv~.-age, data = Boston)
summary (lm.fit1)
lm.fit1=update(lm.fit, ~. -age)
```

#3.6.4 Interaction Terms

#3.6.5 Non-linear Transformations of the Predictors

```{r}
lm.fit2=lm(medv~lstat +I(lstat^2), data = Boston)
summary(lm.fit2)
lm.fit=lm(medv~lstat, data=Boston)
anova(lm.fit ,lm.fit2) #we can see the lm.fit2 fitted better based on F test
par(mfrow=c(2,2))
plot(lm.fit2)

#for checking the polynominal
lm.fit5=lm(medv~ poly(lstat, 5), data = Boston) #fifth order fitted better
summary(lm.fit5)
summary(lm(medv~log(rm), data = Boston))
```

#3.6.6 Qualitative Predictors

```{r}
fix( Carseats )
names(Carseats )
```

#problem

2. Carefully explain the differences between the KNN classifier and KNN
regression methods.

The result of KNN classifier is the classification output for Y (qualitative), while other output for a KNN regression predicts the
quantitative value for f(X). both related in formula.

3.Suppose we have a data set with five predictors, X1 =GPA, X2 = IQ,
X3 = Gender (1 for Female and 0 for Male), X4 = Interaction between
GPA and IQ, and X5 = Interaction between GPA and Gender. The
response is starting salary after graduation (in thousands of dollars).
Suppose we use least squares to fit the model, and get ˆβ0 = 50, ˆβ1 =
20, ˆβ2 = 0.07, ˆβ3 = 35, ˆβ4 = 0.01, ˆβ5 = −10.
(a) Which answer is correct, and why?
i. For a fixed value of IQ and GPA, males earn more on average
than females.
 
ii. For a fixed value of IQ and GPA, females earn more on
average than males.
iii. For a fixed value of IQ and GPA, males earn more on average
than females provided that the GPA is high enough.
iv. For a fixed value of IQ and GPA, females earn more on
average than males provided that the GPA is high enough.

answer:
Y = 50 + 20(gpa) + 0.07(iq) + 35(gender) + 0.01(gpa * iq) - 10 (gpa * gender)
suppose : gpa l1 iq l2
(a) Y = 50 + 20 l1 + 0.07 l2 + 35 gender + 0.01(l1 * l2) - 10 (l1 * gender)
male: (gender = 0)   50 + 20 l1 + 0.07 l2 + 0.01(l1 * l2)
female: (gender = 1) 50 + 20 l1 + 0.07 l2 + 35 + 0.01(l1 * l2) - 10 (l1)

iii. Once the GPA is high enough, males earn more on average.

(b) Predict the salary of a female with IQ of 110 and a GPA of 4.0.

answer:
(b) Y(Gender = 1, IQ = 110, GPA = 4.0)
= 50 + 20 * 4 + 0.07 * 110 + 35 + 0.01 (4 * 110) - 10 * 4
= 137.1

(c) True or false: Since the coefficient for the GPA/IQ interaction
term is very small, there is very little evidence of an interaction
effect. Justify your answer.

answer:
(c) False. We must examine the p-value of the regression coefficient to
understand whether the interaction term is statistically significant or not.

9. This question involves the use of multiple linear regression on the
Auto data set

(d) Use the plot() function to produce diagnostic plots of the linear
regression fit. Comment on any problems you see with the fit.
Do the residual plots suggest any unusually large outliers? Does
the leverage plot identify any observations with unusually high
leverage?

```{r}
library (MASS)
library (ISLR)
data(Auto)
lm.fit1 = lm(mpg~.-name, data=Auto)
summary(lm.fit1)
par(mfrow=c(2,2))
plot(lm.fit1)

#The fit does not appear to be accurate because there is an obvious curve pattern to the residuals plots. From the leverage plot, point 14 appears to have high leverage, without a high magnitude residual.

plot(predict(lm.fit1), rstudent(lm.fit1))

#There are possible outliers regarding  plot of studentized residuals because there are data with a value greater than 3.
```

(e) Use the * and : symbols to fit linear regression models with
interaction effects. Do any interactions appear to be statistically
significant?

```{r}
lm.fit2 = lm(mpg~cylinders*displacement+displacement*weight, data = Auto)
summary(lm.fit2)

#picked two highest correlation pairs from correlation matrix.From the p-values, we can see that the interaction between displacement and weight is statistically signifcant, while the interactiion between cylinders and displacement is not.
```

(f) Try a few different transformations of the variables, such as
log(X),√X, X2. Comment on your findings.

```{r}
lm.fit3 = lm(mpg~log(weight)+sqrt(horsepower)+acceleration+I(acceleration^2), data = Auto)
summary(lm.fit3)
par(mfrow=c(2,2))
plot(lm.fit3)
plot(predict(lm.fit3), rstudent(lm.fit3))

#from the p-values, the log(weight), sqrt(horsepower), and acceleration^2 all have statistical significance. The residuals plot has less of a obvious pattern than the plot of all linear regression terms. The studentized residuals displays potential outliers (>3). The leverage plot indicates more than three points with high leverage.
#The Q-Q plot indicates somewhat unnormality of the residuals. So, a better transformation need to be applied to our model.So in the next attempt, we use log(mpg) as our response variable.


lm.fit2<-lm(log(mpg)~cylinders+displacement+horsepower+weight+acceleration+year+origin,data=Auto)
summary(lm.fit2)
par(mfrow=c(2,2)) 
plot(lm.fit2)
plot(predict(lm.fit2),rstudent(lm.fit2))

#The outputs show that log transform of mpg yield better model fitting regarding better R^2, normality of residuals).
```

10. This question should be answered using the Carseats data set.
(h) Is there evidence of outliers or high leverage observations in the
model from (e)?

```{r}
library(ISLR)
summary(Carseats)
lm.fit2 = lm(Sales ~ Price + US, data = Carseats)
summary(lm.fit2)
plot(predict(lm.fit2), rstudent(lm.fit2))

#All studentized residuals appear to be bounded by -3 to 3, so not outliers 

par(mfrow=c(2,2))
plot(lm.fit2)
#There are a few observations that greatly exceed $(p+1)/n$ (r 3/397) on the leverage-statistic plot that suggest that the corresponding points have high leverage.
```

14. This problem focuses on the collinearity problem.
(a) Perform the following commands in R:
The last line corresponds to creating a linear model in which y is
a function of x1 and x2. Write out the form of the linear model.
What are the regression coefficients?

```{r}
set.seed (1)
x1=runif (100)
x2 =0.5* x1+rnorm (100) /10
y=2+2* x1 +0.3* x2+rnorm (100)
#Y = 2 + 2 X_1 + 0.3 X_2 + \epsilon beta_0 = 2, beta_1 = 2, beta_2 = 0.3 
```

(b) What is the correlation between x1 and x2? Create a scatterplot
displaying the relationship between the variables.

```{r}
cor(x1, x2)
plot(x1, x2)
```

(c) Using this data, fit a least squares regression to predict y using
x1 and x2. Describe the results obtained. What are ˆ β0, ˆ β1, and
ˆ β2? How do these relate to the true β0, β1, and β2? Can you
reject the null hypothesis H0 : β1 = 0? How about the null
hypothesis H0 : β2 = 0?

```{r}
lm.fit = lm(y~x1+x2)
summary(lm.fit)
#beta_0 = 2.1305 , beta_1 = 1.4396, beta_2 = 1.0097
# We can reject the null hypothesis for beta_1 because its p-value is below 5%. We cannot reject the null hypothesis for beta_2 because its p-value is much above the 5%
```
(d) Now fit a least squares regression to predict y using only x1.
Comment on your results. Can you reject the null hypothesis
H0 : β1 = 0?

```{r}
lm.fit = lm(y~x1)
summary(lm.fit)
#Yes, we can reject the null hypothesis for the regression coefficient given the p-value for its t-statistic is near zero.
```

(e) Now fit a least squares regression to predict y using only x2.
Comment on your results. Can you reject the null hypothesis
H0 : β1 = 0?

```{r}
lm.fit = lm(y~x2)
summary(lm.fit)
#Yes, we can reject the null hypothesis for the regression coefficient given the p-value for its t-statistic is near zero.
```
(f) Do the results obtained in (c)–(e) contradict each other? Explain
your answer.

No, because x1 and x2 have collinearity, it is hard to distinguish their effects when regressed upon together.

(g) Now suppose we obtain one additional observation, which was
unfortunately mismeasured.
Re-fit the linear models from (c) to (e) using this new data. What
effect does this new observation have on the each of the models?
In each model, is this observation an outlier? A high-leverage
point? Both? Explain your answers.

```{r}
x1=c(x1 , 0.1)
x2=c(x2 , 0.8)
y=c(y,6)

lm.fit1 = lm(y~x1+x2)
summary(lm.fit1)
lm.fit2 = lm(y~x1)
summary(lm.fit2)
lm.fit3 = lm(y~x2)
summary(lm.fit3)

#In the first model, it shifts x1 to statistically insignificance and shifts x2 to statistiscal significance from the change in p-values between the two linear regressions.

par(mfrow=c(2,2))
plot(lm.fit1)
par(mfrow=c(2,2))
plot(lm.fit2)
par(mfrow=c(2,2))
plot(lm.fit3)
#In the first and third models, the point becomes a high leverage point.

plot(predict(lm.fit1), rstudent(lm.fit1))
plot(predict(lm.fit2), rstudent(lm.fit2))
plot(predict(lm.fit3), rstudent(lm.fit3))

#Looking at the studentized residuals, we don't observe points too far from the 3 value cutoff, except for the second linear regression: y ~ x1.
```